Is it time for an NBA expansion?

### 2024-04-20 paper/paper.qmd
Model Updates

library(tidyverse)
library(readr)
library(modelsummary)
library(tinytex)
```

@@

# Saving Clean Data
write.csv(nba_data, "../data/clean_data/nba_data.csv", row.names = FALSE)
write.csv(full_nba_data, "../data/clean_data/full_nba_data.csv", row.names = FALSE)
```

@@

plot(model_ny)
# Summary of the linear model
msummary(
  list(
    "times Year" = nba_model,
    "Without Year" = model_ny,
    "plus year" = nba_model_2
  ),
  fmt = 2
  )
summary(nba_model)
summary(model_ny)
summary(nba_model_2)
```

@@

>>>>

library(tidyverse)
library(knitr)
library(readr)
library(modelsummary)
library(tinytex)
library(lubridate)
```

@@

# Saving Clean Data
write.csv(nba_data, "../data/clean_data/nba_data.csv", row.names = FALSE) #Only League Averages
write.csv(full_nba_data, "../data/clean_data/full_nba_data.csv", row.names = FALSE) #All Teams

scoring_data$Date <- as.Date(scoring_data$Date)

scoring_data$Year <- year(scoring_data$Date) +
  ifelse(month(scoring_data$Date) > 8 | 
         (month(scoring_data$Date) == 8 & day(scoring_data$Date) > 12), 1, 0)

lebron_data$Season <- as.integer(lebron_data$Season)

@@

plot(model_ny)
# Summary of the linear model
msummary(
  list(
    "times Year" = nba_model,
    "Without Year" = model_ny,
    "plus year" = nba_model_2
  ),
  fmt = 2
  )

summary(model_ny)
summary(nba_model_2)
```

@@

ggplot(scoring_data, aes(x = Year, fill = factor(Year))) +
  geom_histogram(stat = "count", binwidth = 1, color = "black") +
  labs(title = "Frequency of Records by Year",
       x = "Year",
       y = "Count of Records",
       fill = "Year") +
  theme_minimal() +
  theme(legend.position = "none")
##
data_1980_onwards <- scoring_data %>%
  filter(Year >= 1980)

# Create histogram for count of records per year from 1980 onwards
ggplot(data_1980_onwards, aes(x = Year)) +
  geom_histogram(stat = "count", bins = length(unique(data_1980_onwards$Year)), fill = "blue", color = "black") +
  labs(title = "Count of Records per Year from 1980 Onwards",
       x = "Year Modified",
       y = "Count of Records") +
  theme_minimal()

##
data_1980_60pts_plus <- scoring_data %>%
  filter(Year >= 1980, PTS >= 70)

# Create histogram for count of records per year for scores of 60 or more from 1980 onwards
ggplot(data_1980_60pts_plus, aes(x = Year)) +
  geom_histogram(stat = "count", bins = length(unique(data_1980_60pts_plus$Year)), fill = "red", color = "black") +
  labs(title = "Count of Records per Year for Scores of 60+ PTS from 1980 Onwards",
       x = "Year Modified",
       y = "Count of Records") +
  theme_minimal()
```

```{r}

nba_avg_pts <- nba_data %>%
  group_by(Year) %>%
  summarize(Avg_PTS = mean(PTS, na.rm = TRUE))

comparison_data <- lebron_data %>%
  rename(Year = Season) %>%  # Rename Season to Year for merging
  left_join(nba_avg_pts, by = "Year") %>%
  mutate(Ratio = PTS / Avg_PTS)

ggplot(comparison_data, aes(x = Year, y = Ratio)) +
  geom_point(aes(color = Year), size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "navy") +
  labs(title = "LeBron's PTS as a Ratio to NBA Average PTS Across Seasons",
       x = "Season",
       y = "Ratio of LeBron's PTS to NBA Average PTS") +
  theme_minimal()

ggplot(comparison_data, aes(x = Year, y = Ratio, fill = Year)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "LeBron's PTS as a Ratio to NBA Average PTS Across Seasons (Bar Graph)",
       x = "Season",
       y = "Ratio of LeBron's PTS to NBA Average PTS") +
  theme_minimal() +
  theme(legend.position = "none")
